\documentclass[../../../main.tex]{subfiles}
\begin{document}

\subsection{Welcome speech}
What did you just say to me you little rus? I'll have you know that I graduated top of my rustrip team from Easterlake, and I've been involved in numerous rustrips on both Fyn and Zealand, and i have over 300 confirmed chugs. I am trained in left outside alone and I'm the best vector in the entire studystart. You are nothing to but just another rus. I will drink you under the table with a precision of 35 jägerbombs, mark my words. You think you can get away with writing that shit about me in the gossipbox? Think again. As we speak I am contacting my secret network of bums across DTU and your IP is being traced right now so you better prepare to fail math1, maggot. Math1 that wipes the pathetic little thing you call your study. You are fucking dead, kid. I can be anywhere, anytime, and I can use liking on you in over seven hundred ways, and that's just with my bare hands. No only am I extensively trained in unarmed study start dances but I have a ccess to the entire studystartwiki and I will use it to to its full extent to sing your miserable ass up, you little shit. If only you had know what unholy retribution your little ``clever'' gossip was about to bring down upon you, maybe you would have held your fucking tongue. But you didn't, and now you're paying the price, goddamn idiot. I will down starmix from Lyngby to Ballerup and you will drown in it. You're fucking dead, kiddo.

\subsubsection{Presentation of vectors and bums}
Every vector and bums presents themselves. Navn, studyline and semester.
Hver vektor og bums præsenterer sit navn, retning samt semester


\subsubsection{Cabin rules}

\begin{itemize}
    \item \textbf{Smoking}
    Smoking is only allowed at the designated bins we have placed
    
    \item \textbf{Broken stuff}
    Accidents happens - tell your vector
    
    \item \textbf{The beach}
    Take a vector with you if you want to go the the beach
    
    \item \textbf{Danish law}
    Hvis man har glemt at pakke nogle sjove piller eller lignende ud efter Roskilde, så afskaf det. If we find it you are sent home.
    
    
    \item \textbf{Telephone and watch}
    We encourage you to leave it in your room as it provides a more relaxed and pleasant trip
    
    \item \textbf{Shut-up-hand-sign}
    If a vector holds their hand in the air it means that you should stay quiet
    
    \item \textbf{Playbook}
    Everything we have planned is written in them. For your own sake please don't take them.
    
    \item \textbf{Your own alcohol}
    Giv the alcohol to your vector. We will return it once we are back at DTU.
    
    \item \textbf{Vests}
    Presentation of Day and Driver
    
    \item \textbf{Stay on the plot}
    Don't go to far away so we can't find you
    
    \item \textbf{Beverage system}
    
    \textit{Scan your tag, scan your bevrage, scan your multiplier, scan your tag.}
    If you loose your tag tell it to the beverage responsbile and they will give you a new one. It will, however, cost you a beverage. NO OPEN BEVERAGES NEAR THE SWAMP MACHINE!!!!
\end{itemize}

\subsubsection{Bathtub}
There is a tub with a lot of games etc. in it. You are free to use it we ask that you return it in nice condition tho.


\subsubsection{Music}
To listen to your favorite song with Jesu Brødrene you que it. NO OPEN BEVERAGES NEAR THE COMPUTER --- marked with tape.


\subsubsection{Studystart rules}

\begin{itemize}
    \item \textbf{Buffallo}
    The reason why we only chug with our right hand is to pay homage to our cowboy hero Buffalo Bill. See back in the wild west Buffalo bill was the fastest shooter in West Virginia. In the wild west you always had your six shooter sitting on your right hip so you could get to it fast as lightning. One day buffalo bull was sitting in the local saloon with a beer in his right hand. Then in came the worst bandit in the state and he started shooting wildly around him. Buffalo Bill could easily have taken down the bad boy but in surprise he looked down at his right hand and where the beer was. He was simply too slow to put down the beer which ended in him dying. Therefore if you see somebody drinking with their right hand you yell BUFFALO and then the person has to chug his beer so he is able to use his pistol hand in case of bandits. When you chug however you have to use your right hand however so you can use the empty bottle as ammunition.
    
    \textbf{Responsible:} \placeholder
    
    \item \textbf{3 steps}
    If you walk to far away from you beverage others can call ``3 steps'' and then you have only 3 steps to get to you beverage. If you can not do this it results in a chug.
    
    \textbf{Responsible:} \placeholder
    \item \textbf{2 åbne genstande} 

    Hvis du har to åbne genstande må du være virkelig tørstig, så hvorfor ikke lige bunde den ene?
    
    \textbf{Responsible:} \placeholder

    \item \textbf{Divine} 
    If you have just been called out for Buffallo 7 times in the last 10 minutes maybe you feel to pressured. If you stick out your little finger while chugging then sombody else can call divine and help you chug the rest.
    
    \textbf{Responsible:} \placeholder


    \item \textbf{Capsule}
    When you open your beer and a capsule flies away another person can point at the capsule, yell ``capsule'' and count down from 10. If the ``counter'' counts down to 0 before the ``opener'' has reached the capsule then the ``opener'' must chug.
    
    \textbf{Responsible:} \placeholder
    
    \item \textbf{Gentleman's sport}
    The most important rule of all. We must be kind to eachother. Drinking is a gentleman's sport.
\end{itemize}
\end{document}