\documentclass[../../../main.tex]{subfiles}
\begin{document}

\section{Buffer Games}
\begin{multicols}{2}
\subsection*{Frostbox}
    The only rule is that you don't talk about the rules to Frostbox.

\subsection*{Meyer}
    You throw two dice in a cup stacked ontop another without showing the result to the other players. You tell the highest combination of the numbers (i.e. a 2 and 6 gives 62, 5 and 3 gives 53) and give the cups to the next player. The sequence from lowest to higest is: normal kombination of numbers, pairs, small meyer (1 and 3), meyer (1 and 2). If you get 32 you all drink and you get a second chance. You are allowed to lie but you risk that the other players call your bluff. Whenever you pass the cups you \textbf{must} say the exact number of higher than the last. If you call a bluff and lift the cups and you were right the other person drinks, however if you were wrong you drink.

\subsection*{Hygge meyer}
    This is a gentleman's game where the goal of the game is to get the lowest number (same priority system as in standard meyer). The winner gets to chug the glass filled with a beverage from the middle of the table and fills it however much they like. Since this is a gentleman's game your opponents are allowed to throw the dice multiple times if they believe they can do better. This is however limited to 3 times (for the first player). All other players then have that many times to throw the dice as the first player did. The dice goes to all players and afterwards you detimne the winner. If you get a small meyer then you have to chug the drink, fill it again (however much you like) and throw again. If you get a meyer you may give the chug to a different player and they have to fill it (however much they would like). The person who got the meyer has to throw again.
    
    When you pass the dice on you say the number you got to the power of number of throws the first player used (e.g. 43 to the power of 2).
    
\subsection*{Ninjawarrior}
    People stand in a circle. You get one move each turn and try to hit the other players hands. If someone hits your hand you lose it. You are out if you lose both hands. If someone attacks your hand you may flinch (Make one movement out of the way).

\subsection*{Petite}
    Everyone stands in a cirkle and holds each other at the shoulder (like a conga line). You sing "petite, petite, petite petite petite petite" and take a step on the beat. After this you stop and take hold of the next persons shoulder and continue the song. This is continued untill everyone can sit on the thighs of the person behind them.

\subsection*{Over the bridge}
    A player chooses a theme (animals, icy things, Denmark etc.) The others have to guess the theme and asks ``May I take $x$ with me over the bridge?'' If $x$ fits the theme you awnser ``yes'' and ``no'' if it does not. Everyone gets a guess and you continue until the theme is chosen or the players give up.
    
    Here are a few examples of themes:
    
    \begin{itemize}
        \item Something from a motor
        \item Things in a drink
        \item Green items --- or a different colour
        \item Animals with 4 legs
        \item Easily combustible items
    \end{itemize}

\subsection*{Monster game}
    A Vector makes teams. The vector shouts a number of body parts e.g. 3 feet, 5 hands and 1 fabulous ass.
    Now the russes have to coordinate to only have that number of bodyparts on the ground.
    The vector checks if the russes have that exact number of body parts to complete their ``Monster''.


\subsection*{Formation}
    You shout an object e.g. ``HOUSE''
    The other players now have to make a house.
    It is much easier if they make the formation laying down
    The team that does it the quickest wins.
    
\subsection*{Submarines and torpedos}
    Split into small teams, one person monitors the whole game. Each time stands in their own conga line. Everyone on the team except for the one in the rear have their eyes closed. The one in the rear now has to control the team in the direction of the other ``submarines'' and hit them. The one in the rear claps on the right or left should according to which direction the submarine has to move. The claps move forward through the whole line. The ``torpedo'' is send of when the person in the rear claps both shoulders simultaneously, then the person in the front is then shot of like a ``torpedo''. If the ``torpedo'' hits a ``submarine'' that team is now out of the game. You continue until only one team is left.

\subsection*{Evolution game}
    Egg, hammerhead shark, cat, albatros.\\
    You start of by going down in a squat and hop around saying ``egg, egg, egg, egg'' until you find another egg and play rock, paper, scissors. The winner (of one game) gets to evolve to a hammerhead shark.\\
    As a hammerhead shark you swim around hunched with your arms acros your head while saying ``hammer, hammer, hammer, hammer''. To evolve again you play rock, papper, scissors with another hammerhead shark. The winner evolves to a cat that says ``Meow''. \\
    To evolve again you play rock, paper, scissors with another cat.

\subsection*{Mingling game}
    You walk around saying: Mingle, Mingle, Mingle. At some point a number is said, like 5. Then the russes have to go into groups of 5. Those who did not get to form a team is out.

\subsection*{All my chickens come home}
    You stand in a row on one end of the field. In the middle stands the fox. The vector then calls for all that fulfills a theme (e.g. has red shoes) has to come home. Those who fit the theme must run to the other side of th field. The fox must then try to catch those who run. Those who are caught must stand where they are cought in the comming rounds. The last person catched is the winner.

\subsection*{Mother Clutter}
    One person is chosen to be Mother Haywire. The person walks a bit away and closes their eyes. The other holds hands together in a big circle and wraps togther without ever unlocking their hands --- like your wired earbuds left in your pocket. Mother Haywire is called back and gets to fix the mess by getting everyone back to one big circle.

\subsection*{Standing troll}
    A few players (can be just one) are chosen to be the one to catch the others. When caught you have to stand still with your legs spread apart and arms to the side. You are saved by another person crawls through your legs. The person crawling through the others leg has to say their name. An example Peter crawls through Simon's legs. Peter has to say ``Simon''.

\subsection*{Hygge mood}
    Lay down on the ground with your head on eachothers stomach. This is just to spread the hygge mood --- can't really be used as an entertainment.

\subsection*{Frostbox}
    YOU DON'T TALK ABOUT THE RULES TO FROSTBOX!....\\
    But here they are: If they don't know, the game is about finding out the rules as you play. You stand in a circle and takes turns counting. You start by saying "1" then the next person says "2" and so on. At certain numbers you'll say something different. If you mess up, everyone starts over!! Then you'll say "What you said was XX, what you meant was YY" and they slowly learn something. The one who messed up starts the next "1". \\
    If the number is divisible by 5, say "Fum!"\\
    If the number is divisible by 7, say "Bum!" (or "Boom!") and the direction switches! E.g. if it goes "6", "Bum!", then the person who said "6" also has to say "8". \\
    On 12 you say "Fum Bum Sum!" ($5+7=12$ \#QuickMaths) which works like a "Bum!"\\
    On 35 you say "Fum Bum Multiplum!" ($5\cdot7=35$) which also works like a "Bum!". If you make it this far, you are prepared for a "Frostbox" next round. \\
    A Frostbox is an object you add to the circle of players, which is also "counting", but without saying it out loud. You have to imagine it. E.g. if someone just said "3" and it's the frostbox' turn, it'll say "4" (you imagine) and the next person has to say "Fum!". 


\subsection*{Massage mood}
    Create a circle and giv massage to eachother.


\subsection*{Studystart dances}
    \textit{If people need to move about:}
    Pongdance, Birdmachine, Zidansen, Left outside alone, Tamagotchi etc.
    
\subsection*{Beercrocket}
    If people need to drink

\subsection*{Cocio/Beer Hat}
    Place an unopened cocio/beer on your head and stand in a circle.  Now try to knock the other players cocio off their head by throwing a frisbee at them. If the cocio falls for whatever reason, you chuck it. The players are allowed to move but if your hat falls off, you must chug.

\subsection*{Buffalo}
    Everyone sits in a circle and someone starts off by counting and slapping their own shoulder (the shoulder tapped determines the direction).\\\vspace{1em}

\textbf{Special Numbers:}\\
    \textbf{7} - place arms horizontally parallel over the chest and the lower hand shows the direction and they cannot say the number.\\
    \textbf{14} - place arms horizontally parallel over the chest and the upper hand shows the direction and they cannot say the number.\\
    \textbf{21} - make buffalo horns on your head and say buffalo and point at someone and they cannot say the number. The person they point at has to chug their drink and can make a new rule for the next round.\\\vspace{1em}
    
    Every time someone messes up a rule, the counting, the direction, etc. they have to take s sip.


\subsection{Beer Croquet}
    Build a croquet cores, and play as you normally would croquet. When you chug you must also go back to the start of the field and your team has to present an empty bottle/can at the start of your next turn. If you are in possesion of an empty bottle/can you may place a ``mine'', walk into the field and say out loud ``there is mines'' and place the empty bottle/can on the playing field. It must be placed atleast the head of the club away from other objects.While playing, if you hit the gate you must chug and start over. If you let go of the club you must chug and start over. If you hit a mine you must chug and start over. If a team hits their ball while you have the club in hand and not a beverage in the other you must chug and start over. If a mine is tiped you guessed it, chug and start over. On your turn, if you hit another teams ball with your own, you may place your foot atop your own and croquet it away. When you go through a gate you get another turn. If you --- for whatever reaseon --- cannot present an empty bottle/can at the start of your next turn after being sent back to the start you are in the pit. When in the pit you may not play untill you finish your drink.

\end{multicols}

\end{document}