\documentclass[../../../main.tex]{subfiles}
\begin{document}

\subsection{Busride}

\subsubsection{General information about the bus trip}

\begin{description}
\item[Responsible] \placeholder
\item[Time] \placeholder
\item[Duration] \placeholder
\end{description}

The bus responsbile talks with the busdriver about what we are allowed to do on the bus. Is roation for speed dating allowed? May we drink alcohol on the bus? Can we use the bathroom?


\begin{table}[ht!]
\begin{center}
\begin{tabular}{|l|c|c|}
\hline
\textbf{Permission to}  & \textbf{We may :)}    & \textbf{We may not :(}    \\ \hline
Move around in the bus  & $\square$             &  $\square$                \\ \hline
Use the toilet          & $\square$             &  $\square$                \\ \hline
Alcohol                 & $\square$             &  $\square$                \\ \hline
Other beverages         & $\square$             &  $\square$                \\ \hline
Food                    & $\square$             &  $\square$                \\ \hline
Snacks                  & $\square$             &  $\square$                \\ \hline
Music                   & $\square$             &  $\square$                \\ \hline
Microphone              & $\square$             &  $\square$                \\ \hline
\end{tabular}
\end{center}
\end{table}

\textbf{Remember}
\begin{itemize}
    \item Garbage bags by the seats so everyone can get their trash out and other bags for "pant".
    \item Make sure your russes are seated in their teams.
    \item Check off the russes as they enter the bus.
    \item The bus responsible checks the bus for cans and makes sure it looks nice on arrival.
    \item The remaining vectors make sure their cross-teams are led to their sleeping accomodations \VEKTOREX does this for bus responsible's team.
\end{itemize}

\begin{mats}{Saturday}{Bus trip}
    \mat{4}{Packs of beer (can)}
    \mat{2}{Packs of soft drinks (can)}
    \mat{2}{Roll of trashbags bags (small)}
    \mat{1}{Roll of garbage bags (big)}
\end{mats}

\textbf{Tidsplan}
\begin{itemize}
    \item Ca. 5 min - Let people sit down, etc.
    \item Ca. 5 min - Bus speech and distribution of soft drinks
    \item Ca. 10 min - free time
    \item Ca. 30 min - Speeddating
    \item Ca. 15 min - Free time
    \item Ca. 10 min - Tell jokes
\end{itemize}

\textbf{Bus speech}
\begin{itemize}
    \item Welcome
    \item How long the bus trip wil take
    \item Use of toilets
    \item Use the trashbags we brought
    \item Beverages
    \item Bridge toast
\end{itemize}

\textbf{Briiiiiidge tooooast}
As the bus approches a bridge, the responsible vector counts down so that you --- hopefully --- reach 0 when you drive under the bridge. Feel free to add extra constants and the like. An example: 10, 9, 8, 7, 6, 5, 4, $\pi$, 3, Eulers number, 2 $\sqrt{2}$, $i^4$, 0, toast.

\textbf{List of jokes}
\begin{itemize}
    \item Three guys in the desert find a lamp with a genie in it. The genie grants one wish to each of the guys. The first guy wishes to be home. The second guy wishes for the same. The third guys says "It feels kinda lonely here now, i wish the other guys were here"
    \item What is blue and smells like red paint? Blue paint.
    \item What is red and bad for your teeth? A brick
    \item How many apples grow on a tree? All of them!
    \item How do you make a clown cry? You kill his family.
    \item Can a kangaroo jump higher than a house? Of course, houses cant jump at all.
\end{itemize}

\textbf{Speed dating:}\\
You get 1 minute per person and rotate the person sitting on the left side of the bus backwards and the person sitting on the right side one seat forward.
\begin{itemize}
    \item McDonalds or Burger King?
    \item Which is better, cats or dogs.
    \item Would you rather only have shirts that are one size too small or one size too large
    \item What would you prefer: Be allergic to babies or be allergic to elderly people
    \item Would you rather be a reverse centaur or a reverse mermaid?
    \item Would you rather be a character from Harry Potter or a character from Star Wars?
    \item Would you rather never lose your phone or never lose your keys?
    \item Would you rather not eat for two days or eat the same meal for a month?
    \item Would you rather drink one glass of blood or a liter of oil?
    \item Would you rather fart loudly once everytime you have a serious conversation or burp after every kiss.?
    \item Never eat rice or never eat pasta ?
    \item Cursed to be bald forever or always have a bad haircut?
    \item Always mumble or always shout?
    \item Never be able to travel or never be able to stay in one place?
    \item Would you rather vomit uncontrollably for one-minute every time you hear the happy birthday song or get a headache that lasts for the rest of the day every time you see a bird (including in pictures or a video)?
    \item Would you rather be unable to move your body every time it rains or not be able to stop moving while the sun is out?
    \item Would you rather be able to detect any lie you hear or get away with any lie you tell?
    \item Would you rather have no taste buds or be color blind?
    \item Would you rather be the richest person in the world or the smartest?
    \item Would you rather wear a wedding dress/tuxedo every single day or wear a bathing suit every single day?
    \item Would you rather have all dogs try to attack you when they see you or all birds try to attack you when they see you?
    \item Would you rather thirty butterflies instantly appear from nowhere every time you sneeze or one very angry squirrel appear from nowhere every time you cough?
    \item Would you rather live in a cave or live in a tree house?
    \item Would you rather be able to teleport anywhere or be able to read minds?
    \item Would you rather create a great piece of art and not get credit or get credit for a piece of art you didn’t create?
    \item Would you rather age from the neck up or the neck down only?
    \item Would you rather the aliens that make first contact be robotic or organic?
    \item Would you rather lose the ability to read or lose the ability to speak?
    \item Would you rather be covered in fur or covered in scales?
    \item Would you rather be in jail for a year or lose a year off your life?
    \item Would you rather always be 10 minutes late or always be 20 minutes early?
    \item Would you rather be able to talk to land animals, animals that fly, or animals that live under the water?
    \item Would you rather be able to control animals with your mind or control electronics with your mind?
\end{itemize}
\end{document}